---
title: "Week 4 Homework Example"
author: "Nicholas Good"
output:
  html_document: default
  pdf_document: default
---

```{r global_options, include = FALSE}
  knitr::opts_chunk$set(fig.path = 'figures/',
                        warning = FALSE,
                        message = FALSE,
                        fig.width = 6, fig.height = 10,
                        cache = FALSE)
```

---

# Libraries

```{r libraries}
library(tidyverse)
library(knitr)
library(broom)
library(scales)
```

---

# Read homicide data

* use `"../"` because markdown is in the `output` folder

* the `col_types = cols()` prevents warning message

```{r}
raw_data <- read_csv("../data/homicide-data.csv",
                     col_types = cols())
```

---

# Manipulate raw data

* add a column with the city and state combined
* print the first line

```{r}
homicide_data <- raw_data %>%
                 mutate(city_name = paste0(city, ", ", state))
```

```{r, echo = FALSE}
kable(head(homicide_data %>%
      select(city, state, city_name), 1))
```

---

# Unsolved homicides

* fix messy data
* summarise
* organize

```{r}
unsolved <- homicide_data %>%
            filter(!is.na(city)) %>%
            mutate(disposition = sub("<.*", "", disposition),
                   disposition = tolower(gsub(" |/",  "_", disposition)),
                   disposition = factor(disposition)) %>%
            group_by(city_name, disposition) %>%
            summarise(num = n()) %>%
            ungroup() %>%
            spread(disposition, num) %>%
            mutate(n_total = closed_by_arrest +
                             closed_without_arrest +
                             open_no_arrest,
                   n_unsolved = open_no_arrest + closed_without_arrest) %>%
            select(city_name, n_total, n_unsolved)
```

* check

```{r, echo = FALSE}
kable(head(unsolved , 5))
```

---

# Baltimore case study

* create baltimore dataframe

```{r}
baltimore <- unsolved %>%
             filter(city_name == "Baltimore, MD")
```

* run the prop test

```{r}
prop_baltimore <- prop.test(x = baltimore$n_unsolved,
                            n = baltimore$n_total,
                            conf.level = 0.95)
```

* print output of the `prop.test` function:

```{r, echo = FALSE}
prop_baltimore
```

* `tidy` the results

```{r}
prop_baltimore_tidy <- tidy(prop_baltimore)
```

* extract the estimate and confidence interval:

```{r}
kable(prop_baltimore_tidy %>%
      select(estimate, conf.low, conf.high),
      digits = 2)
```

---

# Run on all cities

```{r}
all_cities <- unsolved %>%
              na.omit() %>%
              mutate(prop = map2(n_unsolved, n_total, prop.test),
                     prop_list = map(prop, tidy)) %>%
              unnest(prop_list, .drop = TRUE)
```

# Plot

```{r plot, fig.height = 7, fig.width = 4.5}
all_cities %>% 
  filter(city_name != 'Tulsa, AL') %>% 
  ggplot(aes(x = estimate, y = reorder(city_name, estimate))) +
  geom_point(color = "white") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), 
                 height = 0,
                 color = 'white') +
  theme_dark() +
  labs(x = 'Percent of homicides that are unsolved',
       y = '') +
  scale_x_continuous(labels = percent,
                     limits = c(0.2, 0.8),
                     breaks = seq(0.2,0.8,0.1)) +
  ggtitle('Unsolved homicides by city',
          subtitle = 'Bars show 95% confidence interval')
```
```

